---
title: "R_club_HW6"
author: "Rongkui Han"
date: "May 31, 2017"
output: 
  html_document: 
    keep_md: yes
---

####7.6 Patterns and models
```{r}
library(tidyverse)
library(dplyr)
ggplot(data = faithful) +
  geom_point(mapping = aes(x = eruptions, y = waiting))
library(modelr)
mod = lm(log(price) ~ log(carat), data = diamonds)
diamonds2 = diamonds %>% #to remove the coveriance between price and carat
  add_residuals(mod) %>%
  mutate(resid = exp(resid))
ggplot(data = diamonds2) +
  geom_point(mapping = aes(x = carat, y = resid))
ggplot(data = diamonds2) +
  geom_boxplot(mapping = aes(x = cut, y = resid))
```

Now we can see the price increases (although slightly) with better cuts.

####7.7 ggplot2 calls
```{r}
ggplot(data = faithful, mapping = aes(x = eruptions)) +
  geom_freqpoly(binwidth = 0.25)
ggplot(faithful, aes(eruptions)) +
  geom_freqpoly(binwidth = 0.25) #this is like a short hand that omitted all x=, mapping= , and data= etc. 
```

```{r}
diamonds %>%
  count(cut, clarity) %>%
  ggplot(aes(clarity, cut, fill = n)) +
    geom_tile()
```

###Chapter 10: Tibble  
####10.2 Creating tibbles  
```{r}
as_tibble(iris)
tibble(x = 1:5, y = 1, z = x^2 + y)
tibble(':)' = "smile", ' ' = "space", '2000' = "number")
tribble(~x, ~y, ~z, 
        "a",2,3.6,
        "b",1,8.5) #-_- this is kinda confusing. 
```

####10.3 Tibbles vs. data.frame  
#####10.3.1 Printing 
```{r}
tibble(
  a = lubridate::now() +runif(1e3) * 86400,
  b = lubridate::today() + runif(1e3) * 30,
  c = 1:1e3,
  d = runif(1e3),
  e = sample(letters, 1e3, replace = TRUE)
)
#somehow it didnt print.
library(nycflights13)
flights %>%
  print(n = 10, width = Inf)
#options(tibble.print_max = n, tibble.print_min = m) to change the difalut option of printing 
#options(tibble.width = Inf) to always print all columns. 
nycflights13::flights %>%
  View()
``` 

##### 10.3.2 Subsetting   
```{r}
df = tibble(x = runif(5), y = runif(5))
df$x
df[["x"]] #never used this one before
df[[1]]
df %>% .$x #you can subset in a pipe
df %>% .[["x"]]
```

####10.4 Interacting with older code
```{r}
tb = tibble(x = 1:5, y = c("a","b","c","d","e"))
class(as.data.frame(tb))
```

####10.5 Exercises  
1. How can you tell if an object is a tibble?  
```{r}
mtcars
as.tibble(mtcars)
diamonds
class(mtcars)
mtcars %>%
  is_tibble() #this is kinda cool. 
as.tibble(mtcars) %>%
  is_tibble()
class(diamonds)
```

I don't know I was supposed to be able to tell which one was a tibble just by printing them. But when I uwed the class() function it was pretty clear.   

2. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behavious cause you frustration?  
```{r}
df = data.frame(abc = 1, xyz = "a", xy = "b")
df$x
df$a
#the $ command returns a column with just the first letter only when the first letter is unique to a column. Still this might be problematic. 
df[,"xyz"]
df[,c("abc","xy")]
df_tb = as.tibble(df)
df_tb$a #short hand doesn't work for tibbles. 
df_tb[,"xyz"] # your output is a tibble, not a vector. This is actually really good. 
```

the df$x command gave me the same output as df[,"xyz"]. I guess the "x"" was good enough to evoke "xyz?"  

3. If you have the name of a vairable stored in an object, e.g. var = "mpg", how can you extract the reference variable from a tibble?
```{r}
tbcars = as.tibble(mtcars)
var = "mpg"
tbcars[[var]]
as.data.frame(mtcars)[,var]
```

This is very interesting when looked at side-by-side. Subsetting the tibble "diamonds" with select() gave me the output nicely organized in a column, whereas the subsetting the data frame "diamonds" gave a mass of text (factors).  

4. Practive referring to non-syntactic names in the following data frame by:    
a. Extracting the variable called 1;  
b. Plotting a scatterplot of 1 vs 2;  
c. Creating a new column called 3 which is 2 divided by 1;  
d. Renaming the columns to one, two and three.  
```{r}
annoying = tibble(
  '1' = 1:10,
  '2' = annoying[['1']] * 2 + rnorm(length('1'))
)
#OK the code wouldn't even work. The error message reads: "Error in "1" * 2 : non-numeric argument to binary operator". I think R did not get the '1' part... I don't know what to do. This is truly annoying. 
```

5. What does tibble::enframe() do? When might you use it?   
```{r}
tibble::enframe(c(1:3))
```

I guess it makes a vector into dataframe? I could figure out how the name and value arguments work.  

6. What option controls how many additional column names are printed at the footer of a tibble?  

*I think you use the options() function? But I'm not sure what the question is asking for or how to do it =P. 

