---
title: "R club Note"
author: "Rongkui Han"
date: "April 26, 2017"
output: html_document
---
1. When you use a ` ("tickmark") in front of a line, the knitted document formats that line like a line of code but does not run it.  

2. embeddings in R code chuncks that determine figure dimensions:  
{r fig.with = 7 fid.height = 7} something like this. The unit is in inches.  

3. 
```{r}
ggplot(data = mpg)+
  geom_point(mapping = aes(x = displ, y = hwy), shape = 22, stroke = 15) +
#What does stroke do. It doesn't work on color filled shapes.
ggplot(data = mpg)+
  geom_point(mapping = aes(x = displ, y = hwy), shape = 22, stroke = 15) +
  facet_wrap(drv~cyl)
#what happens when you facet_wrap two variables. Not the preties but might be useful. 
```

4. 
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class == "compact"), shape = 22, stroke = 5) +
  labs(color = "Legend") +
  scale_color_manual(labels = c("Not compact", "compact"), values = c("red","blue"))
#Use labs() and scale_color_manual() to change the text in the legend.
```

5. you can modify plots you already made.

```{r}
plot1  = ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, color = class == "compact"), shape = 22, stroke = 5)
plot1
#Update your plot
plot1 = plot1 + labs(color = "Legend") +
  scale_color_manual(labels = c("Not compact", "compact"), values = c("red","blue"))
```

5/3
install.packages(grid.extra)
grid.arrange(plot1,plot2, width = c(a,b)) can put two plots side by side. 

