---
title: "May_10_HW"
author: "Rongkui Han"
date: "May 10, 2017"
output: 
  html_document: 
    keep_md: yes
---
####5.1.1 Prerequisites  
```{r}
library(nycflights13)
library(tidyverse)
```

####5.1.2  
```{r}
flights
```

####5.2 Filter  
```{r}
filter(flights, month == 1, day == 1)
jan1 = filter(flights, month ==1, day ==1)
dim(jan1)
#I'm just testing if this is the same as subsetting with basic R operations. It looks like they are the same. 
jan1.1 = flights[flights$month == 1 & flights$day ==1,] 
dim(jan1.1)
#putting statement in parentheses makes R print the variable. 
(xmas = filter(flights, month == 12, day == 25))
```

####5.2.1 Comparison  
```{r}
sqrt(2) ^ 2 == 2
1/49 * 49 == 1
near(sqrt(2) ^ 2 , 2)
near(1/49 * 49 , 1)


```

####5.2.2 Logical operators  
```{r}
filter(flights, month == 11 | month == 12)

```

####5.2.4 Exercise  
#####1. Find all flights that   
######1.1 Had an arrival delay of two or more hours  
```{r}
filter(flights, arr_delay >2)
```

######1.2 Flew to Houston (IAH or HOU)  
```{r}
filter(flights, dest == "IAH" | dest =="HOU")
```

######1.3 Were operated by United, American, or Delta  
```{r}
levels(as.factor(flights$carrier))
filter(flights, carrier == "UA" | carrier == "AA" | carrier == "DL")
```

######1.4 Departed in summer (July, August, and September)  
```{r}
filter(flights, month == 7 | month == 8 | month == 9)
```

######1.5 Arrived more than two hours late, but didn’t leave late  
```{r}
filter(flights, arr_delay >2 & dep_delay <= 0)
```

######1.6 Were delayed by at least an hour, but made up over 30 minutes in flight  
```{r}
filter(flights, dep_delay >= 1 & dep_delay-arr_delay > 0.5)
```

######1.7 Departed between midnight and 6am (inclusive)  
```{r}
filter(flights, dep_time <= 600 & dep_time >= 0 | dep_time == 2400)
```

#####2.  
```{r}
flights[between(flights$dep_time, 0, 600),]
#NA's are not removed using this function
```

#####3.
```{r}
table(is.na(flights$dep_time))
naorno = is.na(flights)
tablena = apply(naorno, 2, function(x) table(x))
tablena
```
8255 flights have missing departure time. 
It looks light arrival time (and the correpsonding departure delay, arrival delay and air time) and tail numbers have missing values.   

#####4. 
```{r}
NA^0 # not missing, because the 0th power of anything is 1. 
filter(flights, dep_time == NA | TRUE) # not missing because the "TRUE" option has content
filter(flights, FALSE & NA) # missing because there is no intersection between "unknown" and "false".
NA * 0 # i don't know why this is missing...
```

####5.3 Arrange  
```{r}
arrange(flights, year, month, day)
arrange(flights, desc(arr_time))
```

####5.3.1 Exercise  
#####1.   
```{r}
arrange(flights, !is.na(arr_time))
```

#####2.  
```{r}
arrange(flights, desc(dep_delay))
arrange(flights, dep_time)
```

####3.  
```{r}
arrange(flights, desc(distance/air_time))
```

####4. 
```{r}
arrange(flights, desc(distance)) # longest
arrange(flights, distance) # shortest
```

