---
title: "May_10_HW"
author: "Rongkui Han"
date: "May 10, 2017"
output: 
  html_document: 
    keep_md: yes
---
####5.1.1 Prerequisites  
```{r}
library(nycflights13)
library(tidyverse)
```

####5.1.2  
```{r}
flights
```

####5.2 Filter()
```{r}
filter(flights, month == 1, day == 1)
jan1 = filter(flights, month ==1, day ==1)
dim(jan1)
#I'm just testing if this is the same as subsetting with basic R operations. It looks like they are the same. 
jan1.1 = flights[flights$month == 1 & flights$day ==1,] 
dim(jan1.1)
#putting statement in parentheses makes R print the variable. 
(xmas = filter(flights, month == 12, day == 25))
```

####5.2.1 Comparison  
```{r}
sqrt(2) ^ 2 == 2
1/49 * 49 == 1
near(sqrt(2) ^ 2 , 2)
near(1/49 * 49 , 1)


```

####5.2.2 Logical operators  
```{r}
filter(flights, month == 11 | month == 12)

```

####5.2.4 Exercise  
#####1. Find all flights that   
######1.1 Had an arrival delay of two or more hours  
```{r}
filter(flights, arr_delay >2)
```

######1.2 Flew to Houston (IAH or HOU)  
```{r}
filter(flights, dest == "IAH" | dest =="HOU")
```

######1.3 Were operated by United, American, or Delta  
```{r}
levels(as.factor(flights$carrier))
filter(flights, carrier == "UA" | carrier == "AA" | carrier == "DL")
```

######1.4 Departed in summer (July, August, and September)  
```{r}
filter(flights, month == 7 | month == 8 | month == 9)
```

######1.5 Arrived more than two hours late, but didn’t leave late  
```{r}
filter(flights, arr_delay >2 & dep_delay <= 0)
```

######1.6 Were delayed by at least an hour, but made up over 30 minutes in flight   
```{r}
filter(flights, dep_delay >= 1 & dep_delay-arr_delay > 0.5)
```

######1.7 Departed between midnight and 6am (inclusive)   
```{r}
filter(flights, dep_time <= 600 & dep_time >= 0 | dep_time == 2400)
```

#####2.  
```{r}
flights[between(flights$dep_time, 0, 600),]
#NA's are not removed using this function
```

#####3.
```{r}
table(is.na(flights$dep_time))
naorno = is.na(flights)
tablena = apply(naorno, 2, function(x) table(x))
tablena
```
8255 flights have missing departure time. 
It looks light arrival time (and the correpsonding departure delay, arrival delay and air time) and tail numbers have missing values.   

#####4. 
```{r}
NA^0 # not missing, because the 0th power of anything is 1. 
filter(flights, dep_time == NA | TRUE) # not missing because the "TRUE" option has content
filter(flights, FALSE & NA) # missing because there is no intersection between "unknown" and "false".
NA * 0 # i don't know why this is missing...
```

####5.3 Arrange()  
```{r}
arrange(flights, year, month, day)
arrange(flights, desc(arr_time))
```

####5.3.1 Exercise  
#####1.   
```{r}
arrange(flights, !is.na(arr_time))
```

#####2.  
```{r}
arrange(flights, desc(dep_delay))
arrange(flights, dep_time)
```

#####3.   
```{r}
arrange(flights, desc(distance/air_time))
```

#####4.   
```{r}
arrange(flights, desc(distance)) # longest
arrange(flights, distance) # shortest
```

####5.4 Select()  
```{r}
select(flights, year, month, day)
select(flights, year:day)
select(flights, -(year:day))
select(flights, starts_with("arr"))
select(flights, ends_with("delay"))
select(flights, contains("_"))
rename(flights, tail_num = tailnum)
select(flights, time_hour, air_time, everything())
```

####5.4.1  
#####1. 
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)
select(flights, -(year:day), -sched_dep_time, -sched_arr_time, -(carrier:time_hour))
#somehow i can't think of anything else... 
```

#####2.  
```{r}
select(flights, arr_time, arr_time)# it only appears once. 
```

#####3.   
```{r}
vars <- c("year", "month", "day", "dep_delay", "arr_delay")
#select(flights, vars) this doesn't run because the input vector is in characters, not in factors.
select(flights, one_of(vars)) # one_of() makes the character inputs readable.
```

#####4.  
```{r}
select(flights, contains("TIME"))
#select(flights, contains("TIME"), ignore.case = FALSE)
# this command will turn off ignore.case. 
```

it is actually quite surprising to see that this command worked. I guess the default is case neutral. 

####5.5 Mutate()
```{r}
flights_sml <- select(flights, 
  year:day, 
  ends_with("delay"), 
  distance, 
  air_time
)
mutate(flights_sml,
  gain = arr_delay - dep_delay,
  speed = distance / air_time * 60
)
mutate(flights_sml,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)
transmute(flights,
  gain = arr_delay - dep_delay,
  hours = air_time / 60,
  gain_per_hour = gain / hours
)
transmute(flights,
  dep_time,
  hour = dep_time %/% 100,
  minute = dep_time %% 100
)
```

####Exercise 5.5.2  
#####1.   
```{r}
mutate(flights, 
       dep_time_in.min = dep_time %/% 100 * 60 + dep_time %% 100, 
       sched_dep_time_in.min = sched_dep_time %/% 100 * 60 + sched_dep_time %% 100)
```

#####2.   
```{r}
transmute(flights, air_time, new_air_time = arr_time - dep_time)
#this is not right because the arr_time and dep_time are not in minutes. 
#to translate arr_time and dep_time into minutes:
transmute(flights, air_time, new_air_time = (arr_time %/% 100 * 60 + arr_time %% 100)-(dep_time %/% 100 * 60 + dep_time %% 100))
#well even after I adjusted the units they still are not equal. I feel like the air_time was calculated wrong. 
#to translate the new_air_time into "hour:minute" format:
transmute(flights, air_time, new_air_time = ((arr_time %/% 100 * 60 + arr_time %% 100)-(dep_time %/% 100 * 60 + dep_time %% 100)) %/% 60 * 100 + ((arr_time %/% 100 * 60 + arr_time %% 100)-(dep_time %/% 100 * 60 + dep_time %% 100)) %% 60)
#nope they are still not equal. 
```

#####3.  
```{r}
transmute(flights, dep_time, sched_dep_time, dep_delay)
#I think dep_delay = dep_time (when expressed in minutes) - sched_dep_time (in minutes). To prove that:
flt_delay = transmute(flights, dep_time, sched_dep_time, dep_delay, new_dep_delay = (dep_time %/% 100 * 60 + dep_time %% 100) - (sched_dep_time %/% 100 * 60 + sched_dep_time %% 100), TorF = dep_delay == new_dep_delay)
flt_delay
table(flt_delay$TorF)
# there are a few that are not exactly the same. Upon looking at them we can see that these involve change of day. It would be difficult to fix these. 
```

#####4.  
```{r}
arrange(flights, desc(min_rank(flights$dep_delay)))
?min_rank()
# the documentation states that ties.method is "min". I couldn't really find what that means...
```

#####5.  
```{r}
1:3 + 1:10
# c(1:3) got wrapped around 3.3 times to match the length of c(1:10)
```

#####6.  
```{r}
x = .5
y = 2
cos(x)
sin(x)
tan(x)

acos(x)
asin(x)
atan(x)
atan2(y, x)

cospi(x)
sinpi(x)
tanpi(x)
```

