---
title: "HW_June_7"
author: "Rongkui Han"
date: "June 7, 2017"
output: 
  html_document: 
    keep_md: yes
---
##11 Data Import
####11.1.1 Prerequisites
```{r}
library(tidyverse)
```

###11.2 Getting started
```{r}
read_csv("a,b,c
         1,2,3
         4,5,6")
```

This is a rather interesting (not sure how useful) function. Notice that it is an "_" between "read" and "csv", not the usual ".". Use *enter* to denote change of row (like you would intuitively).   

```{r}
read_csv("The first line of metadata
         The second line of metadata
         x,y,z
         1,2,3", skip = 2)
read_csv("# the line I want to skip
         x,y,z
         1,2,3", comment= "#")
```

Magic!  

The data don't necessarily have colume names. Or the colume names don't have to be specified in the parentheses.   
```{r}
read_csv("1,2,3\n4,5,6", col_names = FALSE)
read_csv("1,2,3\n4,5,6", col_names = c("x","y","z"))
```

You can use *backslash n* in place of *enter*.  

You can even create a table with na in it, using the "na =" option.   
```{r}
read_csv("a,b,c\n1,2,blahblah", na = "blahblah")
```

I am more ammused by "na = "blahblah"" than I am supposed to.   

####11.2.1 Compared to base R  

+ read_csv() can be 10x faster than read.csv() *surprise!*  
+ They produce tibbles  
+ They are more reproducible. Base R functions inherit some behaviors from your operation system and environment variables, so importing codes that works on your computer might not work on someone else's.  

This is actually a really convincing list of reasons.  

####11.2.2 Exercises  
1. Water function would you use to read a file where fields where separated with "|"? *(psv? -- nope)*  

```{r}
read_delim("1|2|3\n4|5|6", col_names = c("x","y","z"), delim = "|")
```

2. Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?  

*Actually all of their options are the same.*  
read_tsv(file, col_names = TRUE, col_types = NULL,  
  locale = default_locale(), na = c("", "NA"), quoted_na = TRUE,  
  quote = "\"", comment = "", trim_ws = TRUE, skip = 0, n_max = Inf,  
  guess_max = min(1000, n_max), progress = show_progress())  
  
3. What are the most important arguments ro read_fwf()?  

*I think the most important arguments are the ones that don't have decult values, like "file =" and "col_positions".   

4. Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you’ll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame?   

*You will need a "quote =" argument.*   
```{r}
read_delim("x,y\n1,'a,b'", delim = ",", quote = "''" )

```

5. Identify what is wrong with each of the following inline CSV files. What happens when you run the code?  

```{r}
read_csv("a,b\n1,2,3\n4,5,6") 
#the third column gets dropped because the first row has only two items.
read_csv("a,b,c\n1,2\n1,2,3,4") 
#The first row has an NA and the fourth item on the second row gets dropped. The problem is that the rows are not of the same length.  
read_csv("a,b\n\"1")
#second item (column b) missing (NA) in the fist row.  
read_csv("a,b\n1,2\na,b")
#idk... second row has the same content at the column names?
read_csv("a;b\n1;3")
#I think this code is trying the use ";" as a delimiter. The correct code for taht purpose would be:
read_delim("a;b\n1;3", delim = ";")
```

###11.3 Parsing a vector  
```{r}
str(parse_logical(c("TRUE","FALSE","NA")))
str(parse_integer(c("1","2","3")))
str(parse_date(c("2010-01-01","1979-10-14")))
parse_integer(c("1","231",".","456"), na = ".")
#a parsing failure example:
x = parse_integer(c("1","231",".","abc","123.45"), na = ".")
x
problems(x) #returns a tibble
```


