---
title: "HW_June_7"
author: "Rongkui Han"
date: "June 7, 2017"
output: 
  html_document: 
    keep_md: yes
---
##11 Data Import
####11.1.1 Prerequisites
```{r}
library(tidyverse)
```

###11.2 Getting started
```{r}
read_csv("a,b,c
         1,2,3
         4,5,6")
```

This is a rather interesting (not sure how useful) function. Notice that it is an "_" between "read" and "csv", not the usual ".". Use *enter* to denote change of row (like you would intuitively).   

```{r}
read_csv("The first line of metadata
         The second line of metadata
         x,y,z
         1,2,3", skip = 2)
read_csv("# the line I want to skip
         x,y,z
         1,2,3", comment= "#")
```

Magic!  

The data don't necessarily have colume names. Or the colume names don't have to be specified in the parentheses.   
```{r}
read_csv("1,2,3\n4,5,6", col_names = FALSE)
read_csv("1,2,3\n4,5,6", col_names = c("x","y","z"))
```

You can use *backslash n* in place of *enter*.  

You can even create a table with na in it, using the "na =" option.   
```{r}
read_csv("a,b,c\n1,2,blahblah", na = "blahblah")
```

I am more ammused by "na = "blahblah"" than I am supposed to.   

####11.2.1 Compared to base R  

+ read_csv() can be 10x faster than read.csv() *surprise!*  
+ They produce tibbles  
+ They are more reproducible. Base R functions inherit some behaviors from your operation system and environment variables, so importing codes that works on your computer might not work on someone else's.  

This is actually a really convincing list of reasons.  

####11.2.2 Exercises  
1. Water function would you use to read a file where fields where separated with "|"? *(psv? -- nope)*  

```{r}
read_delim("1|2|3\n4|5|6", col_names = c("x","y","z"), delim = "|")
```

2. Apart from file, skip, and comment, what other arguments do read_csv() and read_tsv() have in common?  

*Actually all of their options are the same.*  
read_tsv(file, col_names = TRUE, col_types = NULL,  
  locale = default_locale(), na = c("", "NA"), quoted_na = TRUE,  
  quote = "\"", comment = "", trim_ws = TRUE, skip = 0, n_max = Inf,  
  guess_max = min(1000, n_max), progress = show_progress())  
  
3. What are the most important arguments ro read_fwf()?  

*I think the most important arguments are the ones that don't have decult values, like "file =" and "col_positions".   

4. Sometimes strings in a CSV file contain commas. To prevent them from causing problems they need to be surrounded by a quoting character, like " or '. By convention, read_csv() assumes that the quoting character will be ", and if you want to change it you’ll need to use read_delim() instead. What arguments do you need to specify to read the following text into a data frame?   

*You will need a "quote =" argument.*   
```{r}
read_delim("x,y\n1,'a,b'", delim = ",", quote = "''" )

```

5. Identify what is wrong with each of the following inline CSV files. What happens when you run the code?  

```{r}
read_csv("a,b\n1,2,3\n4,5,6") 
#the third column gets dropped because the first row has only two items.
read_csv("a,b,c\n1,2\n1,2,3,4") 
#The first row has an NA and the fourth item on the second row gets dropped. The problem is that the rows are not of the same length.  
read_csv("a,b\n\"1")
#second item (column b) missing (NA) in the fist row.  
read_csv("a,b\n1,2\na,b")
#idk... second row has the same content at the column names?
read_csv("a;b\n1;3")
#I think this code is trying the use ";" as a delimiter. The correct code for taht purpose would be:
read_delim("a;b\n1;3", delim = ";")
```

###11.3 Parsing a vector  
```{r}
str(parse_logical(c("TRUE","FALSE","NA")))
str(parse_integer(c("1","2","3")))
str(parse_date(c("2010-01-01","1979-10-14")))
parse_integer(c("1","231",".","456"), na = ".")
#a parsing failure example:
x = parse_integer(c("1","231",".","abc","123.45"), na = ".")
x
problems(x) #returns a tibble
```

####11.3.1 Numbers  
```{r}
#you can specify decimal marks via parse_double() 
parse_double("1.23")
parse_double("1,23", locale = locale(decimal_mark = ","))
#parse_number() ignores all non-numeric symbols.
parse_number("$100")
parse_number("20%")
#the combination of parse_number() and parse_double deals with grouping mark.
parse_number("$123,456,789")
parse_number("123.456.789", locale = locale(grouping_mark = "."))
parse_number("123'456'789", locale = locale(grouping_mark = "'"))
```

####11.3.2 Strings  
```{r}
charToRaw("Hadley")
x1 <- "El Ni\xf1o was particularly bad this year"
x2 <- "\x82\xb1\x82\xf1\x82\xc9\x82\xbf\x82\xcd"
parse_character(x1, locale = locale(encoding = "Latin1"))
parse_character(x2, locale = locale(encoding = "Shift-JIS"))
guess_encoding(charToRaw(x1))
guess_encoding(charToRaw(x2))
```

####11.3.3 Factors  
```{r}
fruit = c("apple","banana")
parse_factor(c("apple","banana","bananana"), levels = fruit)
```

####11.3.4 Dates, date-times, and times  
```{r}
parse_datetime("2010-10-01T2010")
parse_datetime("20101010")
parse_date("2010-10-01")
parse_time("01:10 am")
parse_time("20:10:01")
parse_date("01/02/15","%m/%d/%y")
parse_date("01/02/15","%d/%m/%y")
parse_date("01/02/15","%y/%m/%d")
parse_date("1 janvier 2015", "%d %B %Y", locale = locale("fr"))
```

####11.3.5 Exercises
1. What are the most important arguments to locale()?  
```{r, eval = FALSE}
locale(date_names = "en", date_format = "%AD", time_format = "%AT",
  decimal_mark = ".", grouping_mark = ",", tz = "UTC",
  encoding = "UTF-8", asciify = FALSE)
```

All of them look pretty important... it's hard for me to decide which ones are the most important...   

2.What happens if you try and set decimal_mark and grouping_mark to the same character? What happens to the default value of grouping_mark when you set decimal_mark to “,”? What happens to the default value of decimal_mark when you set the grouping_mark to “.”?   
```{r, eval = FALSE}
parse_double("123,456,789", locale = locale(decimal_mark = ",", grouping_mark = ","))
```

There was an error message telling me that decimal_mark and grouping_mark must be different.   
```{r}
parse_double("123456,789", locale = locale(decimal_mark = ","))
```

I guess the default changes?  

```{r}
parse_double("123.456.789", locale = locale(grouping_mark = "."))
```

Changing grouping_mark to "."" did not work for me.   

3. What do date_format and time_formate options to locale do?  
 *I couldn't figure this out.*  
 
 4. If you live outside the US, create a new locale object tjat encapsulates the settings for te types of file you read most commonly. 
 
 *Couldn't figure out how to do this either = =*  
 
 5. What's the difference between read_csv() and read_csv2()?
 *read_csv2() uses ";" instead of comma to delimit.*  
 
 6. What are the most common encodings used in Europe? What are teh most common encodings used in Asia? Do some googling to find out.  
 *IEC 8859 is used for most European languages, and GB 18030 is used in China. EUC is used in Japan.*  
 
7. Generate the correct formate strong to parse peach of the following dates and times:  
```{r}
d1 <- "January 1, 2010"
parse_date(d1, "%B %d, %Y")
d2 <- "2015-Mar-07"
parse_date(d2, "%Y-%b-%d")
d3 <- "06-Jun-2017"
parse_date(d3, "%d-%b-%Y")
d4 <- c("August 19 (2015)", "July 1 (2015)")
parse_date(d4, "%B %d (%Y)")
d5 <- "12/30/14" # Dec 30, 2014
parse_date(d5, "%m/%d/%y")
t1 <- "1705"
parse_time(t1, "%H%M")
t2 <- "11:15:10.12 PM"
parse_time(t2, "%I:%M:%OS %p")
```

###Parsing a file  
####11.4.1 Strategy  
```{r}
guess_parser("2010-10-01")
guess_parser("15:01")
guess_parser(c("TRUE","FALSE"))
guess_parser(c("1","5","9"))
guess_parser(c("12","352","561"))
str(guess_parser ("2010-10-10"))

```

####11.4.2 Problems  
```{r}
challenge = read_csv(readr_example("challenge.csv"))
problems(challenge)
challenge <- read_csv(
  readr_example("challenge.csv"), 
  col_types = cols(
    x = col_integer(),
    y = col_character()
  )
)
challenge <- read_csv(
  readr_example("challenge.csv"), 
  col_types = cols(
    x = col_double(),
    y = col_character()
  )
)
tail(challenge)
challenge <- read_csv(
  readr_example("challenge.csv"), 
  col_types = cols(
    x = col_double(),
    y = col_date()
  )
)
tail(challenge)
```

####11.4.3 Other strategies  
```{r}
challenge2 = read_csv(readr_example("challenge.csv"), guess_max = 1001)
challenge2
challenge2 <- read_csv(readr_example("challenge.csv"), 
  col_types = cols(.default = col_character())
)
df <- tribble(
  ~x,  ~y,
  "1", "1.21",
  "2", "2.32",
  "3", "4.56"
)
df
type_convert(df)
```

###11.5 Writing to a file  
```{r}
write_csv(challenge, "challenge.csv")
challenge
read_csv("challenge.csv")
write_rds(challenge, "challenge.rds")
read_rds("challenge.rds")
```


