---
title: "HW_June_14"
author: "Rongkui Han"
date: "June 14, 2017"
output: 
  html_document: 
    keep_md: yes
---
```{r}
library(tidyverse)
```

###12.2 Tidy data  

There interrelated rulws which make a dataset tidy:  
1. Each variable bust have its own column.  
2. Each observation must have its own row.  
3. Each value must have its own cell.  

####12.2.1 Exercises  
1. Using prose (?), describe how the variables and observations are organized in each sample table.  
 *table1: Each variable has a column and each observation has a row.*  
*table2: the two vatiables "cases" and "population" shared a column.*  
*table3: the values for cases and population shared a column.*  
*table4: could be merged into one table.*  

2. Compute the rate for table2, and table4a + table 4b. You will need to perform four operations:  
  1. Extract the number of TB cases per country per year.  
  2. Extract the matching population per country per year.  
  3. Divide cases by population, and multiply by 10000.  
  4. Store back in the appropriate place.  
Which representation is easiest to work with? Which is hardest? Why?  
```{r}
#tables 1 & 2
table1 = tibble("country" = c("Afghanistan", "Afghanistan","Brazil","Brazil","China","China"), "year" = c(1999,2000,1999,2000,1999,2000), "cases" = c(745, 2666, 37737, 80488, 212258, 213766), "population" = c(19987371,20595360, 172006362, 174504898, 1272915272, 1280428583),"rate" = c(0.373, 1.294, 2.194, 4.612, 1.667, 1.669))
table1
table2 = tibble("country" = c("Afghanistan", "Afghanistan","Afghanistan", "Afghanistan","Brazil","Brazil","Brazil","Brazil","China","China", "China","China"), "year" = c(1999,1999,2000,2000,1999,1999,2000,2000,1999,1999,2000,2000), "type" = c("cases","population", "cases","population","cases","population","cases","population", "cases","population","cases","population"), "count" = c(745, 19987371, 2666, 20595360, 37737, 172006362, 80488, 174504898, 212258, 1272915272, 213766, 1280428583))
table2
t1cases = table1["cases"]
t1cases
t2cases = table2[table2$type=="cases","count"]
t2cases
t1pop = table1["population"]
t1pop
t2pop = table2[table2$type=="population","count"]
t2pop
t1rate = t1cases/t1pop * 10000
t1rate
t2rate = t2cases/t2pop * 10000
t2rate
table1[["new.rate"]] = t1rate
info = tibble("country" = c("Afghanistan", "Afghanistan","Brazil","Brazil","China","China"), "year" = c(1999,2000,1999,2000,1999,2000), "type" = c("rate", "rate", "rate", "rate", "rate", "rate"))
info = cbind(info,t2rate)
table2 = rbind(table2, info)
##table 4
table4a = tibble("county" = c("Afghanistan","Brazil","China"), "`1999`" = c(745, 37737, 212258), "`2000`" = c(2666, 80488, 213766))
table4a
table4b = tibble("county" = c("Afghanistan","Brazil","China"), "`1999`" = c(19987371,172006362,1272915272), "`2000`" = c(20595360,174504898,1280428583))
table4b
rate1999 = table4a[["`1999`"]]/table4b[["`1999`"]] 
rate2000 = table4a[["`2000`"]]/table4b[["`2000`"]] 
table4c = tibble("county" = c("Afghanistan","Brazil","China"), "`1999`" = rate1999, "`2000`" = rate2000)
```

table 2 is very painfrul to work with, especially when I was trying to incorporate the generated data back to the original table. tables 4a and 4b are pretty bad too. A lot of copying and pasting was involved.  

3. Recreat the plot showing change in cases over time using table2 instead of table1. What do you need to do first?  
```{r}
library(ggplot2)
ggplot(table1, aes(year, cases)) + 
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))
```

I first need to subset table 2 and get all the cases counts.   
```{r}
table2cases = table2[table2$type == "cases",]
table2cases
ggplot(table2cases, mapping = aes(year, count)) +
  geom_line(aes(group = country), colour = "grey50") + 
  geom_point(aes(colour = country))
```

####12.3.1 Gathering  
```{r}
table4a
#table4a %>%
#  gather(`1999`, `2000`, key = "year", value = "cases")
#Didn't work for me =(
#table4b %>%
#  gather(`1999`, `2000`, key = "year", value = "population")
#Error: object `1999` not found
```
####12.3.2 Spreading  
```{r}
spread(table2, key = type, value = count)
```

####12.3.3 Exercises
1. Why are gather() and spread() not perfectly symmetrical? Carfully consider the following example:  
```{r}
stocks <- tibble(
  year   = c(2015, 2015, 2016, 2016),
  half  = c(   1,    2,     1,    2),
  return = c(1.88, 0.59, 0.92, 0.17)
)
stocks
stocks %>% 
  spread(year, return) %>% 
  gather("year", "return", `2015`:`2016`)
```

For gather(), you need to specify more than one columns to gather together, and give it a designated column name. For spread() you only need to specify one column to separate, and the new column names are contained in the original column already.  

```{r}
?spread()
```

It sounds like this concerns the type of the value... but i'm not entirely sure.  

2. Why does this code fail?  
```{r, eval = FALSE}
table4a %>% 
  gather(1999, 2000, key = "year", value = "cases")
```

1999 and 2000 need to be `1999` and `2000`

3. Why does spreading this tibble fail? How could you add a new column to fix it?  
*I think it might be because there are two Phillip Woods + age combos with different age values. I can fix it by adding a column the differ in value for the duplicated entries.*    
```{r}
people <- tribble(
  ~name,             ~key,    ~value,
  #-----------------|--------|------
  "Phillip Woods",   "age",       45,
  "Phillip Woods",   "height",   186,
  "Phillip Woods",   "age",       50,
  "Jessica Cordero", "age",       37,
  "Jessica Cordero", "height",   156
)
people %>%
  group_by(name,key) %>%
  mutate(thing = row_number()) %>% #smart
  spread(key = key, value = value)
```

4. Tidy the simple tibble below. Do you need to spread or gather it? Whhat are teh variables?  
```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)
preg %>%
  gather(male, female, key = "gender", value = "count")
```

I gathered it but i'm not sure if that's all I can do.  

###12.4 Separating and uniting  

####12.4.1 Separate  
```{r}
table3 = tibble("country" = c("Afghanistan", "Afghanistan","Brazil","Brazil","China","China"), "year" = c(1999,2000,1999,2000,1999,2000), "rate" = c("745/19987371","2666/20595360" , "37737/172006362", "80488/174504898", "212258/1272915272", "213766/1280428583"))
table3 %>%
  separate(rate, into = c("cases","population"))
table3 %>%
  separate(rate, into = c("cases","population"), sep = "/")
table3 %>%
  separate(rate, into = c("cases","population"), convert = TRUE)
table5 = table3 %>%
  separate(year, into = c("century","year"), sep = 2)
```

####12.4.2 Unite  
```{r}
table5 %>%
  unite(new, century, year, sep = "")
```

####12.4.3Exercises   
1. What do the `extra` and `fill` arguments do in `separate()`? Experiment with the various options for the following two toy datasets.   
```{r}
?separate()
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"))
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "drop")
tibble(x = c("a,b,c", "d,e,f,g", "h,i,j")) %>% 
  separate(x, c("one", "two", "three"), extra = "merge")
tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"))
tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "left")
tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "right")
```

2. Both `unite()` and `separate()` have a `remove` argument. What does it do? Why would you set it to `FALSE`?  
```{r}
tibble(x = c("a,b,c", "d,e", "f,g,i")) %>% 
  separate(x, c("one", "two", "three"), fill = "right", remove = FALSE)
```

It removes the new table from the original table. If you set it to FALSE you will get a table that is a combination of the original and the transformed table.  

3. Compare and contrast `separate()` and `extract()`. Why are there three variations of separation (by position, by separator and with groups), but only one unite? 

```{r}
?extract()
tibble(x = c("a,b,c", "d,e,f", "g,h,i")) %>% 
  extract(x, c("A","B","C"), "([[:alnum:]]+),([[:alnum:]]+),([[:alnum:]]+)")
tibble(x = c("a,b,c", "d,e,f", "g,h,i")) %>% 
  extract(x, c("A","B","C"), "(.),(.),(.)")
```

Super complcated with "regular expression" involved. It is useful for separating out chunks of a complex name (separated by different things). 
