---
title: "Mydata_May3"
author: "Rongkui Han"
date: "May 3, 2017"
output: html_document
---

```{r}
mydata = read.csv("/Users/apple/Desktop/UC_Davis/R_club/Rclub-r4ds_Rongkui.Han/R-club-Apr-26/Qtrimm.stat.csv")
View(mydata)
mydata = mydata[,-1]
mydata$TR.percent = mydata$Trimmed.reads/mydata$In.reads
mydata$TB.percent = mydata$Trimmed.bases/mydata$In.bases
mydata$KR.percent = 1 - mydata$TR.percent
mydata$KB.percent = 1 - mydata$TB.percent
lane = c(rep("A",12), rep("B",12),rep("C",12), rep("D",12),rep("E",12),rep("F",8))
mydata = cbind(mydata,lane)
platecol = c(rep(c(1,2,3,4,5,6,7,8,9,10,11,12),5),1,2,3,4,5,6,7,8)
mydata = cbind(mydata, platecol)
library(tidyverse)
```

#####First I want to take a look at how the base numbers relate to the read numbers.  
```{r}
ggplot(data = mydata) +
  geom_point(mapping = aes(x = In.reads, y = In.bases))
```

It looks like they have a strict linear relationship, which probably means that there are a fix number of base pairs per RNA read. Now we are going to figure out what that number is:
```{r}
model = lm(mydata$In.bases ~ mydata$In.reads)
model
```
From the simple linear regression model we can see that there is approximately 50 base pairs in a read.  

#####Second, we want to see the distribution of percentage of bases kept after the trimming process by each lane where the RNA-seq was done.
```{r}
ggplot(data = mydata) +
  geom_violin(mapping = aes(x = lane, y = KR.percent), trim = FALSE)
```

#####Then we can do a similar analysis to see if there is a column effect.
```{r}
mydata$platecol = as.factor(mydata$platecol)
ggplot(data = mydata) +
  geom_violin(mapping = aes(x = platecol, y = KR.percent), trim = FALSE)
```

This is an interesting plot. It looks like centain columns generate RNA reads with more stable qualities than others. 


