---
title: "HW_June_28"
author: "Rongkui Han"
date: "June 28, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r}
library(tidyverse)
library(nycflights13)
```

###13.3 Keys   

Checking for unique keys (primary keys):  
```{r}
planes %>%
  count(tailnum) %>%
  filter(n>1)

weather %>%
  count(year, month, day, hour, origin) %>%
  filter(n > 1)
``` 

Or the lack thereof:  
```{r}
flights %>%
  count(year, month, day, flight) %>%
  filter(n > 1)
flights %>%
  count(year, month, day, tailnum) %>%
  filter(n > 1)
```

####13.3.1 Exercises    
1. Add a surrogate key to flights.  
```{r}
?row_number()
primary_flights = flights %>%
  mutate(surrogate_key = row_number(flight))
primary_flights
```
2. Identify the keys in the following datasets:  
```{r}
head(Lahman::Batting)
Lahman::Batting %>%
  count(playerID) %>%
  filter(n > 1) #foreign key? Not a primary key.
Lahman::Batting %>%
  count(teamID) %>%
  filter(n > 1) #foreign key? Not a primary key.

ggplot2::diamonds
#There is no primary key (unique identifier) in this table. 
```

3.   
```{r}
head(Lahman::Batting)
head(Lahman::Master)
head(Lahman::Managers)
Lahman::Master %>%
  count(playerID) %>%
  filter(n>1)
Lahman::Batting %>%
  count(playerID) %>%
  filter(n>1)
Lahman::Managers %>%
  count(playerID) %>%
  filter(n>1)
```

Both Batting and Managers contain the foreign key "playerID" that is a primary keys in Master.   

###13.4 Mutating joins  
```{r}
flights2 = flights %>%
  select(year:day, hour, origin, dest, tailnum, carrier)
flights2 %>%
  select(-origin, -dest) %>%
  left_join(airlines, by = "carrier")
flights2 %>% #this is the equivalent of the left_join() function
  select(-origin, -dest) %>%
  mutate(name = airlines$name[match(carrier, airlines$carrier)])
```

####13.4.6 Exercises   
1. Compute the average delay by destination, then join on the airports data frame so you can show the spatial distribution of delays.  
```{r}
head(flights)
avg_delay = flights %>%
  group_by(dest) %>%
  summarise(avg.delay = mean(arr_delay, na.rm = TRUE))
avg_delay
airports %>%
  left_join(avg_delay, c("faa" = "dest")) %>%
  ggplot(aes(lon, lat)) +
    borders("state") +
    geom_point(aes(colour = avg.delay), size = 0.1) +
    coord_quickmap()
```

2. Add the location of the origin and destination (i.e. the lat and lon) to flights.  
```{r}
flight.loc = flights %>%
  left_join(airports, c("dest" = "faa"))
head(flight.loc)
```

3. Is there a relationship between the age of a plane and its delays?  
```{r}
flight.age = flights %>%
  left_join(planes, by = "tailnum") %>%
  mutate(delay = arr_delay/air_time)
head(flight.age)
colnames(flight.age)
ggplot(flight.age, aes(x = year.y, y = delay)) +
  geom_point()
```

Looks like newer planes are more likely to get delayed.  

4. What weather conditions make it more likely to see a delay?  
```{r}
flights.weather = flights %>%
  left_join(weather, by = c("year", "month", "day" , "hour"))
head(flights.weather)
ggplot(flights.weather, aes(x = wind_speed, y = arr_delay)) +
  coord_cartesian(xlim = c(0, 100)) +
  geom_point()
ggplot(flights.weather, aes(x = wind_gust, y = arr_delay)) +
  coord_cartesian(xlim = c(0, 100)) +
  geom_point(aes(colour = wind_dir))
ggplot(flights.weather, aes(x = wind_dir, y = arr_delay)) +
  geom_point() 
ggplot(flights.weather, aes(x = temp, y = arr_delay)) +
  geom_point(aes(colour = humid)) 
```

I can't seem to find any trends.  

5. What happened on June 13 2013? Display the spatial pattern of delays, and then use Google to cross reference with the weather.  
```{r}
flights.weather %>% 
  filter(year == 2013 & month == 6 & day == 13) %>%
  summarise(mean(arr_delay, na.rm = TRUE))
flights.weather %>% 
  summarise(mean(arr_delay, na.rm = TRUE))
```

The mean delay time on June 13, 2013 is 10x the average delay time across all flights in the year of 2013. According to google, there was a heavy storm in NYC on that day. 

###13.5 filtering joins
```{r}
top_dest = flights %>%
  count(dest, sort = TRUE) %>%
  head(10)
top_dest
flights %>%
  filter(dest %in% top_dest$dest) #amazing. This %in% thing. 
```

```{r}
flights %>%
  semi_join(top_dest) #Even more amazing.
```

####13.5.1 Exercises   
1. What does it mean for a flight to have a missing tailnum? What do the tail numbers that don’t have a matching record in planes have in common? (Hint: one variable explains ~90% of the problems.)  
```{r}
missing.tail = flights %>%
  anti_join(planes, by = "tailnum")
head(missing.tail)
ggplot(missing.tail) +
  geom_bar(aes(carrier))
```

It *looks* like their tailnumbers all start with "N", but this is unsolicited observation...  

2. Filter flights to only show flights with planes that have flown at least 100 flights.   
```{r}
flights %>%
  count(tailnum) %>%
  filter(n > 100)
```

3. Combine fueleconomy::vehicles and fueleconomy::common to find only the records of the most common models.  
```{r}
#install.packages("fueleconomy")
library(fueleconomy)
fueleconomy::vehicles %>%
  semi_join(fueleconomy::common)
```

4. Find the 48 hours (over the course of the whole year) that have the worst delays. Cross-reference it with the weather data. Can you see any patterns?  
```{r}
head(flights)
ggplot(flights, aes(x = time_hour, y = arr_delay)) +
  coord_cartesian(ylim = c(450,1250)) +
  geom_point()
```

Can't find it.  

5. What does anti_join(flights, airports, by = c("dest" = "faa")) tell you? What does anti_join(airports, flights, by = c("faa" = "dest")) tell you?  
```{r}
nodest = anti_join(flights, airports, by = c("dest" = "faa")) 
levels(as.factor(nodest$dest))
```

This says that in the flight13 dataset there are four airports whose data are missing from the airports table.   

```{r}
head(anti_join(airports, flights, by = c("faa" = "dest")))
```

This says there are a lot of airports that do not have direct flights with airports in NYC.  

6. You might expect that there’s an implicit relationship between plane and airline, because each plane is flown by a single airline. Confirm or reject this hypothesis using the tools you’ve learned above.  

```{r}
tail_carrier = flights %>%
  count(tailnum, carrier, sort = TRUE)
tail = flights %>%
  count(tailnum, sort = TRUE)
tail_carrier %>%
  anti_join(tail, by = c("n", "tailnum"))
```

Looks like there are 41 planes flown by more than one airlines.  
