---
title: "Chapter 15 & 16"
output: 
  html_document: 
    keep_md: yes
---

#Chapter 15: Factors  

##15.1.1 Prerequisites  
```{r}
library(tidyverse)
library(forcats)
```

##15.2 Crearing factors  
```{r}
x1 = c("Dec","Apr","Jan","Mar")
x2 = c("Dec","Apr","Jam","Mar")
month_levels = c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")
y1 = factor(x1, levels = month_levels)
y1
sort(y1) #wow sorts in the order of the reference levels vector. 
y2 = parse_factor(x2, levels = month_levels) #gives warning for typo.
```

```{r}
factor(x1) #w/o "levels=" input, levels are automatically sorted in alphabetical order.
f1 = factor(x1, levels = unique(x1)) #order of levels match the order of first appearance in the dataset
f1

f2 = x1 %>% factor() %>% fct_inorder() #order of levels match the order of first appearance. 
f2

levels(f2)
```

##15.3 General Social Survey  
```{r}
head(gss_cat)
gss_cat %>%
  count(race)
ggplot(gss_cat, aes(x = race)) +
  geom_bar()
ggplot(gss_cat, aes(x = race)) +
  geom_bar() +
  scale_x_discrete(drop = FALSE)
```

###15.3.1 Exercise    
1. Explore the distribution of rincome (reported income). What makes the default bar chart hard to understand? How could you improve the plot?  

```{r}
gss_cat %>%
  count(rincome)
ggplot(gss_cat, aes(x = rincome)) +
  geom_bar() +
  theme(text = element_text(size = 10), axis.text.x = element_text(angle = 45, hjust = 1))
```

*The original bar chart is confusing because the lower income is on the right side of the x axis.* This can be fixed by manually ordering the levels in rincome.   

```{r}
level = names(table(gss_cat$rincome))[order(names(table(gss_cat$rincome)))]
ggplot(gss_cat, aes(x = factor(rincome, levels = level))) +
  geom_bar() +
  theme(text = element_text(size = 10), axis.text.x = element_text(angle = 45, hjust = 1))
```

2. What is the most common relig in this survey? What’s the most common partyid?  
 
```{r}
ggplot(gss_cat) +
  geom_bar(aes(x = relig)) +
  theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) #Protestant
ggplot(gss_cat) +
  geom_bar(aes(x = partyid)) +
  theme(text = element_text(size = 10), axis.text.x = element_text(angle = 45, hjust = 1)) #independent
```

3. Which relig does denom (denomination) apply to? How can you find out with a table? How can you find out with a visualisation?  
```{r}
#Find out with a table:
by_relig = group_by(gss_cat, relig)
summarise(by_relig, Denomination = n_distinct(denom)) #Checking how many demoninations are under each religion.

#Find out with visualization:
ggplot(gss_cat) +
  geom_bar(aes(x = relig , fill = denom)) +
  theme(axis.text.x = element_text(size = 10, angle = 45, hjust = 1)) # Christians and Protestants
```

## 15.4 Modifying factor order  

```{r}
relig_summary = gss_cat %>%
  group_by(relig) %>%
  summarise(
    age = mean(age, na.rm = TRUE),
    tvhours = mean(tvhours, na.rm = TRUE),
    n = n()
  )
ggplot(relig_summary, aes(x = tvhours, y = relig)) + geom_point() # people who don't knwo what their religions are tend to watch more TV...?
```

After reordering the y axis by the values on the x axis:  

```{r}
ggplot(relig_summary, aes(x = tvhours, y = fct_reorder(relig, tvhours))) + geom_point()
```

We can do the same thing by creating a separate coloumn. I like the previous method better tho:  

```{r}
relig_summary %>%
  mutate(relig = fct_reorder(relig, tvhours)) %>%
  ggplot(aes(tvhours, relig)) +
  geom_point()
```

```{r}
rincome_summary = gss_cat %>%
  group_by(rincome) %>%
  summarise(age = mean(age, na.rm = TRUE), tvhours = mean(tvhours, na.rm = TRUE), n = n())

ggplot(rincome_summary) +
  geom_point(aes(x = age, y = fct_reorder(rincome, age)))

ggplot(rincome_summary) +
  geom_point(aes(x = age, y = fct_relevel(rincome, "Not applicable"))) #put "Not applicable" at the front of the list. 
```

```{r}
by_am = gss_cat %>%
  filter(!is.na(age)) %>% #filter(!is.na()) is very smart
  group_by(age, marital) %>%
  count()
by_age = gss_cat %>%
  group_by(age) %>%
  count()
by_am
by_age
colnames(by_age) = c("age","N")
by_am = merge(by_am, by_age)
by_am = by_am %>%
  mutate(prop = n/N)

ggplot(by_am, aes(age, prop, colour = marital)) +
  geom_line(na.rm = TRUE)

ggplot(by_am, aes(age, prop, colour = fct_reorder2(marital, age, prop))) +
  geom_line() +
  labs(colour = "marital")

gss_cat %>%
  mutate(marital = marital %>% fct_infreq() %>% fct_rev()) %>% #dont know what really happened here but ok.
  ggplot(aes(marital)) +
  geom_bar()
```

###15.4.1 Exercises  

1. There are some suspiciously high numbers in tvhours. Is the mean a good summary?

*maybe not...?*

2. For each factor in gss_cat identify whether the order of the levels is arbitrary or principled.

```{r}
colnames(gss_cat)
levels(gss_cat$year)
levels(gss_cat$marital)
levels(gss_cat$rincome)
```

Don't know the answer to the questions...  

3. Why did moving “Not applicable” to the front of the levels move it to the bottom of the plot?  

Because the front of the list is the closest to the x-axis.  

###15.5 Modifying factor levels  

```{r}
gss_cat %>%
  count(partyid)
gss_cat %>%
  mutate(partyid = fct_recode(partyid,
      "Republican, strong" = "Strong republican",
      "Republican, weak"      = "Not str republican",
      "Independent, near rep" = "Ind,near rep",
      "Independent, near dem" = "Ind,near dem",
      "Democrat, weak"        = "Not str democrat",
      "Democrat, strong"      = "Strong democrat")) %>%
  count(partyid)

gss_cat %>%
  mutate(partyid = fct_recode(partyid,
    "Republican, strong"    = "Strong republican",
    "Republican, weak"      = "Not str republican",
    "Independent, near rep" = "Ind,near rep",
    "Independent, near dem" = "Ind,near dem",
    "Democrat, weak"        = "Not str democrat",
    "Democrat, strong"      = "Strong democrat",
    "Other"                 = "No answer",
    "Other"                 = "Don't know",
    "Other"                 = "Other party"
  )) %>%
  count(partyid)
```

```{r}
gss_cat %>%
  mutate(partyid = fct_collapse(partyid,
    other = c("No answer", "Don't know", "Other party"),
    rep = c("Strong republican", "Not str republican"),
    ind = c("Ind,near rep", "Independent", "Ind,near dem"),
    dem = c("Not str democrat", "Strong democrat")
  )) %>%
  count(partyid)
```

```{r}
gss_cat %>%
  mutate(relig = fct_lump(relig)) %>%
  count(relig)
```

```{r}
gss_cat %>%
  mutate(relig = fct_lump(relig, n= 10)) %>%
  count(relig, sort = TRUE) %>%
  print()
```

```{r}
by_partyage = gss_cat %>%
  mutate(partyid = fct_recode(partyid,
    "Republican, strong"    = "Strong republican",
    "Republican, weak"      = "Not str republican",
    "Independent, near rep" = "Ind,near rep",
    "Independent, near dem" = "Ind,near dem",
    "Democrat, weak"        = "Not str democrat",
    "Democrat, strong"      = "Strong democrat",
    "Other"                 = "No answer",
    "Other"                 = "Don't know",
    "Other"                 = "Other party"
  )) %>%
  group_by(age, partyid) %>%
  count()
by_partyage
by_age = gss_cat %>%
  group_by(age) %>%
  count()
by_age
colnames(by_age)[2] = "N"

by_partyage = merge(by_partyage, by_age)
by_partyage
by_partyage %>%
  mutate(prop = n/N) %>%
  ggplot(aes(x = age , y = prop, colour = partyid)) +
    geom_line()
```

2. How could you collapse rincome into a small set of categories?

*I know how to do this. Too much typing.*


